\documentclass[25pt, , innermargin=-1in, blockverticalspace=0in]{tikzposter}
\geometry{papersize={36in, 24in}}
\usepackage{theme}
\usepackage[backend=biber,style=numeric]{biblatex}

\addbibresource{poster.bib}

\usetheme{RITTheme}

\title{Autonomous Navigation for Mobile Robots}
\author{Sagar Khadse | Zack Butler}

\begin{document}
  \maketitle
  \begin{columns}
    \column{.25}
    \block{Abstract}{
      Mobile Robots are developed to be able to move in an environment and 
      perform specific tasks such as warehouse robots moving packages and 
      stocking shelves efficiently. GPS can help when navigating in outdoor
      environments but fails when used indoors. These robots need to be able to 
      sense their environment while also being able to self localize itself in 
      the environment for efficient path planning. An autonomous navigation 
      system avoids the need to manually program the robot path and allows the 
      robot to handle minor changes in the environment. This project aims to 
      implement Simultaneous Localization and Mapping using a RGBD camera 
      mounted on top of a robot base.
    }
    \block{Objectives}{
      \begin{enumerate}
        \item Researching available SLAM algorithms that could be used for this 
        application and selecting the best fit.
        \item Selecting an indoor environment and generate a 3D map.
        \item Testing localization of the mobile robot within the generated map 
        while navigating through it.
      \end{enumerate}
    }
    \column{.25}
    \block{Architecture}{
      this is the abstract.
    }
    \column{.5}
    \block{Mapping}{
      this is the abstract.
    }
  \end{columns}

  \node [above right, minimum width=\textwidth, minimum height=2in, 
  align=right, fill=titlebgcolor, text=titlefgcolor] 
    at (bottomleft) {
      \begin{minipage}{\linewidth}
        \printbibliography[heading=none]
      \end{minipage}
    };
\end{document}